Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-25 arxiv/proof_gaussian_case.tex
wip

>>>>

\paragraph{Notations.}
Define the index sets
$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
 We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$. Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
 \be\label{labelZ}
 Z^{(1)}= (Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z^{(2)}= (Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee

Moreover, we also define the following averaged resolvents, which are the (weighted) partial traces of $G$:
\be\label{defm}
\begin{split}
m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
 m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z) .
\end{split}
\ee
We will show that these averaged resolvents satisfy some deterministic self-consistent equations asymptotically, which will be the core part of the proof. We refer the reader to the discussions below \eqref{0self_Gii} and \eqref{0self_Gmu1}.
